Active Learning : From Blackbox To Timed Connectors

### 2015-12-27 paper/paper.tex
semantics of fifo

% declaration of environments
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

@@

\subsection{Parameterized Mealy Machine}
\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle S(\Sigma), s_0,
  \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an alphabet to its corresponding Mealy Machine.
  \begin{itemize}
    \item[-] $\Sigma$ is a \emph{finite} input/output alphabet
    \item[-] $S$ is a function that maps a \emph{finite} alphabet to a \emph{finite} set of
      states. We use $S(\Sigma)$ to denote the state set.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
    \item[-] $\delta$ 
  \end{itemize}
\end{definition}

@@

>>>>

% declaration of environments
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}

@@

@@

\subsection{Parameterized Mealy Machine}
\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle
  S(\Sigma), s_0, I(\Sigma), O(\Sigma), \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
  alphabet to its corresponding Mealy Machine. 
  \begin{itemize}
    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereafter referred to as an alphabet)
    \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
      states. We use $S(\Sigma)$ to denote the state set.
    \item[-] $I(\Sigma)$ maps an alphabet to a set of input actions.
    \item[-] $O(\Sigma)$ maps an alphabet to a set of output actions.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
    \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
      $\delta(\Sigma):S(\Sigma)\times I(\Sigma)\rightarrow O(\Sigma)$ to denote the output function.
    \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
      $\lambda(\Sigma):S(\Sigma)\times I(\Sigma)\rightarrow S(\Sigma)$ to denote the transiton
      function.
  \end{itemize}
\end{definition}

Now we can use Parameterized Mealy Machines to define a new semantics to Reo.
\begin{example}[PMM Semantics of FIFO channel $PM_{FIFO}$]
  The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
    \item[-] $I(\Sigma)=\{(A:d)|d\in\Sigma\cup \{\bot\}\}$
    \item[-] $O(\Sigma)=\{(B:d)|d\in\Sigma\cup\{\bot\}\}$
    \item[-] transition function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d) \\
          q_d & s=q_{d'}\land i=(A:d) \\
          q_0 & s=q_d\land i=(A:\bot) \\
        \end{array}
        \right.
      \end{displaymath}
    \item[-] output function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d) \\
          q_d & s=q_{d'}\land i=(A:d) \\
          q_0 & s=q_d\land i=(A:\bot) \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

\begin{figure}[h]
  \begin{center}
    \input{./images/pmmfifo.tex}
  \end{center}
  \caption{PMM-based Semantics of FIFO, where $\Sigma=\{a,b\}$}
  \label{fig:pmmfifo}
\end{figure}

\todo{finish the definition ..}
\begin{definition}[Production of Parameterized Mealy Machines]
  Now we're going to define the production of two parameterized mealy Machine
  \[
  Prod(PM_1,PM_2)=PM_3
  \]
  as follows,
  \begin{itemize}
    \item[-] $\forall\Sigma,PM_3.I(\Sigma)=PM_1.I(\Sigma)\cup PM_2.I(\Sigma)$
    \item
  \end{itemize}
\end{definition}
